ray

### 2022-03-19 outputs/paper/ray.Rmd
sexornt mental health

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(haven)
library(tidyverse)
library(ggplot2)
```

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(haven)
library(tidyverse)
library(ggplot2)
library("readxl")
library(dplyr)
library(tidyverse)
library(vtable)

@@

sexual orientation

```{r}
sexornt_data <- raw_data %>% select(c(sexornt, hlthmntl)) %>% filter(!is.na(sexornt), !is.na(hlthmntl)) %>%
  mutate(sexornt = case_when(
    sexornt <= 2 ~ "LGBTQ+",
    sexornt == 3 ~ "Heterosexual",
  )) %>%
  mutate(mntl_poor = case_when(
    hlthmntl <= 3 ~ 'Good',
    hlthmntl >= 4 ~ 'Not Good',
  ))

sexornt_data %>% ggplot(aes(x= mntl_poor,  group=sexornt))+
  geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") +
  geom_text(aes( label = scales::percent(..prop..),
                 y= ..prop.. ), stat= "count", vjust = -.5) +
  labs(y = "Percent", fill="mntl_poor") +
  facet_grid(~sexornt) +
  scale_y_continuous(labels = scales::percent)
```
